Create year end summaries

### 2023-02-22 src/year-end-summary.Rmd
Fixed duplicate listing in year-end-summary.Rmd

```{r}
# Create yaml header
create_yaml <- function(yyyy) {
  glue(
    '---
     title: "Pages written in 2022"
     source: new
     date: {yyyy}-12-31
     categories:
     - Blog post
     tags:
     - Website details
     output: html_document
     ---')
}
```

@@

  if (n_year > 0) {print(problem_files)}
  print(problem_files)

>>>>

```{r}
# Create yaml header
create_yaml <- function(yyyy) {
  glue(
    '---
     title: "Pages written in {yyyy}"
     source: new
     date: {yyyy}-12-31
     categories:
     - Blog post
     tags:
     - Website details
     output: html_document
     ---')
}
```

@@

  if (n_year > 0) {print(problem_files)}
